### 2015-01-09 paper_20_sdo.tex
new version of PDF and some minor other changes
remove some stuff

\subsection{THE SOFTWARE DEVELOPMENT LIFECYCLE}
    For this question, I choose to rewrite that section of the proposal.  This was
    my favorite question. It forced me to go look back into the history of
    software development.

    The discipline of software engineering has created a workflow for developing
    software.  
    This workflow is called the \textit{Software Development Life Cycle (SDLC)}.
    SDLC can be defined as \cite{Ruparelia2010}:
    \begin{quote}
     [...] a conceptual framework or process that considers the structure of the stages
     involved in the development of an application from its initial feasibility study
     through to its deployment in the field and maintenance.
    \end{quote}
    While the SDLC states what needs to be done, there are numerous models 
    that formalize exactly how to perform the SDLC.  The models contain
    steps that are commonly referred to as a phases. A few of the popular
    models are described below.

@@

        \begin{figure}
            \centering
            \includegraphics[scale=.5]{images/benington_waterfall.PNG}
            \caption[Benington's original diagram for producing large software systems]
                    {Benington's original diagram for producing large software 
                        systems, adapted from \cite{Benington1987}}
            \label{fig:benington}
        \end{figure}%
        \begin{figure}
            \centering
            \includegraphics[scale=.5]{images/royce_waterfall.PNG}
            \caption[Royce's version of the waterfall model]
                {Royce's version of the waterfall model for producing software 
                        systems, adapted from \cite{Royce1987}}
            \label{fig:royce}
        \end{figure}

        The modern version of the waterfall model specifies that each phase needs 
        to be entirely completed before moving
        onto the next phase.  Some small amount of overlap is permitted and looping 
        occurs but both actions are discouraged and should be limited.  
        A modern diagram of the waterfall model can be seen in Figure \ref{fig:waterfall}.
        \begin{figure}[here]
            \centering
            \includegraphics[scale=.6]{images/waterfall.png}
            \caption[Modern Waterfall]
                {Modern Waterfall Diagram, adapted from \cite{Hibbs2009} }
            \label{fig:waterfall}
        \end{figure}

@@

Check these book \cite{Jones2009, Jones1996, Lee2003}. This might be similar
to process mining \cite{vanderAalst2012}.

>>>>

\subsection{THE SOFTWARE DEVELOPMENT LIFECYCLE}
    The discipline of software engineering has created a workflow for developing
    software.  
    This workflow is called the \textit{Software Development Life Cycle (SDLC)}.
    SDLC can be defined as \cite{Ruparelia2010}:
    \begin{quote}
     [...] a conceptual framework or process that considers the structure of the stages
     involved in the development of an application from its initial feasibility study
     through to its deployment in the field and maintenance.
    \end{quote}
    While the SDLC states what needs to be done, there are numerous models 
    that formalize exactly how to perform the SDLC.  The models contain
    steps that are commonly referred to as a phases. A few of the popular
    models are described below.

@@

        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.5]{images/benington_waterfall.PNG}
            \caption[Benington's original diagram for producing large software systems]
                    {Benington's original diagram for producing large software 
                        systems, adapted from \cite{Benington1987}}
            \label{fig:benington}
        \end{figure}%
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.5]{images/royce_waterfall.PNG}
            \caption[Royce's version of the waterfall model]
                {Royce's version of the waterfall model for producing software 
                        systems, adapted from \cite{Royce1987}}
            \label{fig:royce}
        \end{figure}

        The modern version of the waterfall model specifies that each phase needs 
        to be entirely completed before moving
        onto the next phase.  Some small amount of overlap is permitted and looping 
        occurs but both actions are discouraged and should be limited.  
        A modern diagram of the waterfall model can be seen in Figure \ref{fig:waterfall}.
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.6]{images/waterfall.png}
            \caption[Modern Waterfall]
                {Modern Waterfall Diagram, adapted from \cite{Hibbs2009} }
            \label{fig:waterfall}
        \end{figure}

@@

Check these book \cite{Jones2009, Jones1996, Lee2003}.
